Implementing Real-Time Transport Services over an Ossified Network

### 2016-05-23 paper.tex
Space saving

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than the traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.

@@

These changes could address many of the transport service needs we have for
real-time applications, but still leave a critical issue of how to improve
timing behaviour. Specifically, how to enable partial reliability for TCP,
after which it is possible to layer-on support for managing deadlines and
dependencies.

@@

When a TCP segment is to be retransmitted, the current mapping between its
sequence number and application-level sequence numbers is used to determine
which messages within the segment are to be retransmitted. A liveness check
is performed on these messages, to determine that (i) the message will
arrive on time to be played out; and (ii) the message does not depend on an
expired message. For (i), we combine the time that the message has spent in
a sending queue, with an estimate of the round-trip time and the current
play-out delay. This is then compared against the lifetime of the message,
as expressed by the application. For (ii), we maintain metadata about
sequence numbers that have expired, and check this metadata for the
dependency expressed by the application.

>>>>

The TCP congestion control algorithm is executed by the end points, and
can be changed, provided the new version requires no new information to
be exchanged.
\todo{expand, and discuss how this evolution has occurred to date}
We note that, while standardised TCP congestion control has followed the
goal of maximising throughput at the expense of latency and variability,
this is not required by the protocol. TCP Vegas \cite{brakmo:1994:tcp-vegas}
is perhaps the best known approach that changes these constraints, with a
delay-based algorithm that reduces latency. It would also be possible to
implement alternatives that seek stability, or compatibility with the
dictates of a video codec, rather than traditional ``TCP Friendly''
congestion control -- even if implemented within TCP.

@@

These changes could address many of the transport service needs for
real-time applications, but still leave a critical issue of how to improve
timing behaviour. Specifically, how to enable partial reliability for TCP,
after which it is possible to layer-on support for managing deadlines and
dependencies.

@@

When a TCP segment is to be retransmitted, the mapping between its
sequence number and application-level sequence numbers is used to determine
which messages within the segment are to be retransmitted. A liveness check
is performed on these messages, to determine that (i) the message will
arrive on time to be played out; and (ii) the message does not depend on an
expired message. For (i), we combine the time that the message has spent in
a sending queue, with an estimate of the round-trip time and the current
play-out delay. This is then compared against the lifetime of the message,
as expressed by the application. For (ii), we maintain metadata about
sequence numbers that have expired, and check this metadata for the
dependency expressed by the application.
